### 2017-10-28 monograph/thesis/chapters/introduction.tex
Removed the good coding sections due no references existent.
Removed the unrelated references from the first paragraph at
monograph/thesis/chapters/introduction.tex
Removed the good coding sections due no references existent. (reverted from commit 7d22ff9126a579af14c9159cfe65b2f8750c9d21)
Created 3 new references and referenced the introduction.tex first
paragraph. References:
Style Analysis for Source Code Plagiarism Detection
Learning Natural Coding Conventions
Comparison of open source tools for project management

    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{industrialApplication}

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for
    discoursing. So in this work implementation tool called `Object Beautifier'
    specifically dedicates on how to perform the best layout/display of
    programming code on the computer screen, so that maximize and facilitate the
    understanding of same. Therefore, allowing the programmer to disperse more
    tempe thinking about its coding algorithms problem, other than trying to
    decipher the information that is presented to it on the screen through
    infinit different code layouts. \cite{programIndentation}

    % TODO, put reference for this
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub-questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{independentFramework}

    % TODO, put reference for this
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.
    \cite{architectureFormatting}

    % TODO, put reference for this
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas. \cite{prettyPrinting}

    % TODO, put reference for this
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain-text' mode. Since for code sharing, it is vital for you
    to use a versioning control system which enable project manager\s and
    programmers themselves, take control of their code changes. It does allow to
    easily perform the tracking of code changes and allow you to better
    understand what each programmer is doing every time he formalizes a change
    in the code through a `commit', as in `git' systems for example.
    \cite{massMaintenance}

    % TODO, put reference for this (ref coding\_horror)
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did. Hence, if every
    programmer re-writes the history making changes like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines (ref find\_some). \cite{legacyAssets}

    % TODO, put reference for this
    Talking about the last thing pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re-adding new lines before each one of your beloved if\s, just because some
    night shift programmer had just removed them? \cite{softwarePortfolio}

@@

    \section{How to Deal with}

@@

    Copying and pasting them probably the most straight forward idea, which is
    nice if you are going to it only a few times in a life time like two or
    three. However if you are going to do it move often than these limits,
    please don\q t do that. It is bad for the planet and is worsening your
    health for nothing other than more headaches.

@@

    On preceding example, the `rebuild\_workspace.sh' script is located on the
    testing folder `/cygdrive/c/Test', then when calling it we get some folders
    removed, a file unpacked on the current folder, and our code synced from the
    versioning system directly to testing environment.

>>>>

    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same. Therefore,
    allowing the programmer to disperse more tempe thinking about its coding
    algorithms problem, other than trying to decipher the information that is
    presented to it on the screen through infinit different code layouts.

    % TODO, put reference for this
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub-questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention.

    % TODO, put reference for this
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.

    % TODO, put reference for this
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas.

    % TODO, put reference for this
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain-text' mode. Since for code sharing, it is vital for you
    to use a versioning control system which enable project manager\s and
    programmers themselves, take control of their code changes. It does allow to
    easily perform the tracking of code changes and allow you to better
    understand what each programmer is doing every time he formalizes a change
    in the code through a `commit', as in `git' systems for example.

    % TODO, put reference for this (ref coding\_horror)
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did. Hence, if every
    programmer re-writes the history making changes like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines (ref find\_some).

    % TODO, put reference for this
    Talking about the last thing pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re-adding new lines before each one of your beloved if\s, just because some
    night shift programmer had just removed them?

    \cite{codePlagiarismDetection}
    \cite{softwarePortfolio}
    \cite{legacyAssets}
    \cite{massMaintenance}
    \cite{prettyPrinting}
    \cite{architectureFormatting}
    \cite{independentFramework}
    \cite{programIndentation}
    \cite{industrialApplication}
    \cite{toolsForProjectManagement}

@@

    \section{Common Tasks}

@@

    Copying and pasting them probably the most straight forward idea, which is
    nice if you are going to it only a few times in a life time like two or
    three. However if you are going to do it move than these limits,
    please don\q t do that. It is bad for the planet and is worsening your
    health for nothing other than more headaches.

@@

    On preceding example, the `rebuild\_workspace.sh' script is located on the
    testing folder `/cygdrive/c/Test', then when calling it we get some folders
    removed, a file unpacked on the current folder, and our code synced from the
    versioning system directly to testing environment. You can read more about
    `rsync' utility on \citeonline{synchronizingFolders}.

### 2017-10-28 monograph/thesis/postexto/abstracts.tex
Created 3 new references and referenced the introduction.tex first
paragraph. References:
Style Analysis for Source Code Plagiarism Detection
Learning Natural Coding Conventions
Comparison of open source tools for project management

    \item \textbf{Powerful code indenter front-end, UniversalIndentGUI}: Ever
    concerned about how your code looks like? Ever heard of different indenting
    styles, for example K\&R? Ever received code from someone else who didn't
    care about code formatting? Ever tried to configure a code indenter to
    convert such code to your coding style? Ever got bored by that tedious
    "changing a parameter"-"call the indeter"-"try and error" procedure? Help is
    close to you. UniversalIndentGUI offers a live preview for setting the
    parameters of nearly any indenter. You change the value of a parameter and
    directly see how your reformatted code will look like. Save your beauty
    looking code or create an anywhere usable batch/shell script to reformat
    whole directories or just one file even out of the editor of your choice
    that supports external tool calls.

@@

    \item \textbf{Towards a Universal Code Formatter through Machine Learning}:
    There are many declarative frameworks that allow us to implement code
    formatters relatively easily for any specific language, but constructing
    them is cumbersome. The first problem is that “everybody” wants to format
    their code differently, leading to either many formatter variants or a
    ridiculous number of configuration options. Second, the size of each
    implementation scales with a language’s grammar size, leading to hundreds of
    rules. In this paper, we solve the formatter construction problem using a
    novel approach, one that automatically derives formatters for any given
    language without intervention from a language expert. We introduce a code
    formatter called CODEB UFF that uses machine learning to abstract formatting
    rules from a representative corpus, using a carefully designed feature set.
    Our experiments on Java, SQL, and ANTLR grammars show that CODEB UFF is
    efficient, has excellent accuracy, and is grammar invariant for a given
    language. It also generalizes to a 4th language tested during manuscript
    preparation. \cite{universalCodeFormatter}

@@

>>>>

    \item \textbf{Powerful code indenter front-end, UniversalIndentGUI}: Ever
    concerned about how your code looks like? Ever heard of different indenting
    styles, for example K\&R? Ever received code from someone else who didn't
    care about code formatting? Ever tried to configure a code indenter to
    convert such code to your coding style? Ever got bored by that tedious
    "changing a parameter"-"call the indeter"-"try and error" procedure? Help is
    close to you. UniversalIndentGUI offers a live preview for setting the
    parameters of nearly any indenter. You change the value of a parameter and
    directly see how your reformatted code will look like. Save your beauty
    looking code or create an anywhere usable batch/shell script to reformat
    whole directories or just one file even out of the editor of your choice
    that supports external tool calls. \cite{Schweitzer}

@@

    \item \textbf{Towards a Universal Code Formatter through Machine Learning}:
    There are many declarative frameworks that allow us to implement code
    formatters relatively easily for any specific language, but constructing
    them is cumbersome. The first problem is that “everybody” wants to format
    their code differently, leading to either many formatter variants or a
    ridiculous number of configuration options. Second, the size of each
    implementation scales with a language’s grammar size, leading to hundreds of
    rules. In this paper, we solve the formatter construction problem using a
    novel approach, one that automatically derives formatters for any given
    language without intervention from a language expert. We introduce a code
    formatter called CODEB UFF that uses machine learning to abstract formatting
    rules from a representative corpus, using a carefully designed feature set.
    Our experiments on Java, SQL, and ANTLR grammars show that CODEB UFF is
    efficient, has excellent accuracy, and is grammar invariant for a given
    language. It also generalizes to a 4th language tested during manuscript
    preparation. \cite{universalCodeFormatter}.

@@

    \item \textbf{The Command Line Interface}: This is a very exciting chapter.
    While command line interfaces (CLIs) may not have the cachet of modern
    graphical user interfaces (GUIs), especially those of phones or tablets, the
    CLI is still a remarkably useful and effective user interface. This chapter
    details the design and implementation of the command line interface for
    pdCalc. By the end of this chapter, we will, for the first time, have a
    functioning (albeit feature incomplete) calculator, which is a significant
    milestone in our development. \cite{commandLineInterface}

    \item \textbf{Quantification of interface visual complexity}: Designers
    strive for enjoyable user experience (UX) and put a significant effort into
    making graphical user interfaces (GUI) both usable and beautiful. Our goal
    is to minimize their effort: with this purpose in mind, we have been
    studying automatic metrics of GUI qualities. These metrics could enable
    designers to iterate their designs more quickly. We started from the
    psychological findings that people tend to prefer simpler things. We then
    assumed visual complexity determinants also determine visual aesthetics and
    outlined eight of them as belonging to three dimensions: information amount
    (visual clutter and color variability), information organization (symmetry,
    grid, ease-of-grouping and prototypicality), and information
    discriminability (contour density and figure-ground contrast). We
    investigated five determinants (visual clutter, symmetry, contour density,
    figure-ground contrast and color variability) and proposed six associated
    automatic metrics. These metrics take screenshots of GUI as input and can
    thus be applied to any type of GUI. We validated the metrics through a user
    study: we gathered the ratings of immediate impressions of GUI visual
    complexity and aesthetics, and correlated them with the output of the
    metrics. The output explained up to 51\% of aesthetics ratings and 50\% of
    complexity ratings. This promising result could be further extended towards
    the creation of tLight, our automatic GUI evaluation tool.
    \cite{quantificationOfInterface}

    \item \textbf{Synchronizing folders with rsync}: In this post I cover the
    basics of rsync, in preparation for a subsequent post that will cover
    backups and it's use in conjunction with cronjobs to automatize the backup
    process. From the copying and synchronization of local files and folders, to
    it's use for transfer information among computers. Its use as a daemon when
    SSH is unavailable was moved to it's own section.
    \cite{synchronizingFolders}

    \item \textbf{Comparison of open source tools for project management}:
    Software projects often fail, because they are not adequately managed. The
    establishment of effective and efficient project management practices still
    remains a key challenge to software organizations. Striving to address these
    needs, "best practice" models, such as, the Capability Maturity Model
    Integration (CMMI) or the Project Management Body of Knowledge (PMBOK), are
    being developed to assist organizations in improving project management.
    Although not required, software tools can help implement the project
    management process in practice. In order to provide comprehensive, low-cost
    tool support for project management, specifically, for small and medium
    enterprises (SMEs), in this paper we compare the most popular
    free/open-source web-based project management tools with respect to their
    compliance to PMBOK and CMMI for Development (CMMI-DEV). The results of this
    research can be used by organizations to make decisions on tool adoptions as
    well as a basis for evolving software tools in alignment with best practices
    models. \cite{toolsForProjectManagement}

    \item \textbf{Learning Natural Coding Conventions}: Every programmer has a
    characteristic style, ranging from preferences about identifier naming to
    preferences about object relationships and design patterns. Coding
    conventions define a consistent syntactic style, fostering readability and
    hence maintainability. When collaborating, programmers strive to obey a
    project’s coding conventions. However, one third of reviews of changes
    contain feedback about coding conventions, indicating that programmers do
    not always follow them and that project members care deeply about adherence.
    Unfortunately, programmers are often unaware of coding conventions because
    inferring them requires a global view, one that aggregates the many local
    decisions programmers make and identifies emergent consensus on style. We
    present NATURALIZE, a framework that learns the style of a codebase, and
    suggests revisions to improve stylistic consistency. NATURALIZE builds on
    recent work in applying statistical natural language processing to source
    code. We apply NATURALIZE to suggest natural identifier names and formatting
    conventions. We present four tools focused on ensuring natural code during
    development and release management, including code review. NATURALIZE
    achieves 94\% accuracy in its top suggestions for identifier names. We used
    NATURALIZE to generate 18 patches for 5 open source projects: 14 were
    accepted. \cite{naturalCodingConventions}

    \item \textbf{Style Analysis for Source Code Plagiarism Detection}:
    Plagiarism has become an increasing problem in higher education in recent
    years. A number of research papers have discussed the problem of plagiarism
    in terms of text and source code and the techniques to detect it in various
    contexts. There is a variety of easy ways of copying others’ work because
    the source code can be obtained from online source code banks and textbooks,
    which makes plagiarism easy for students. Source code plagiarism has a very
    specific definition, and Parker and Hamblen define plagiarism on software as
    “A program that has been produced from another program with a small number
    of routine transformations”. The transformations can range from very simple
    changes to very difficult ones, which can be one of the six levels of
    program modifications that are given by Faidhi and Robinson. Coding style is
    a way to detect source code plagiarism because it relates to programmer
    personality without affecting the logic of a program, and can be used to
    differentiate between different code authors. This paper reviews a number of
    publications which report style comparison to detect source code plagiarism
    in order to determine research gaps and explore areas where this approach
    can be improved. A summary of the plagiarism techniques in which style
    analysis can help identify plagiarism is presented.
    \cite{codePlagiarismDetection}
